\textsf{Are frontier models superhuman chemists?}

### 2024-03-12 src/tex/ms.tex
work on main text

@@

>>>>

Because the text used in scientific settings is different from typical natural language, many models have been developed that deal with such text in a special way.
For instance, Galactica\cite{taylor2022galactica} uses special tokenization or encoding procedures for molecules or equations.
To support this, chembench is designed to encode the semantic meaning of various parts of the question or answer.  
For instance, molecules represented in \gls{smiles} are encapsulated in \texttt{[START\_SMILES][\textbackslash END\_SMILES]}.

Because many widely utilized systems do only provide access to text completions (and not the raw model outputs), chembench is designed to operate on text completions.
This is also important with the growing number of tool-augmented systems that use external tools such as search \glspl{api} or code executors.\cite{schick2024toolformer, karpas2022mrkl, yao2022react}
In those cases, the \gls{llm} that returns the probabilities for various tokens (that are conventionally used for model evaluations) is only a part of the whole system, and it is not clear how to interpret the probabilities in the context of the whole system.
The text completions, however, are the final outputs of the system that would also be used in a real-world application (e.g., in a copilot system for chemists).

To understand the current capabilities of \glspl{llm} in the chemical sciences, we evaluated a wide range of models on the chembench corpus, including systems augmented with external tools.
An overview of the results of this evaluation is shown in \Cref{fig:all_questions_models_completely_correct_radar}.

% Bar chart

@@

% Radar chart
To obtain a more detailed understanding of the performance of the models, we also analyzed the performance of the models on different topics.
